A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
K2 facility

A quick \emph{a priori} estimate of the background blended ecipsing
binary rate serves as a good sanity check.  A query to the TRILEGAL
(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
line-of-sight simulation software reveals that the typical density of
field stars along the line of sight to the C1 field is about
$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
0.16 that a background star might be blended within a 8\,arcsec radius
(two pixels) from a target star.  Allowing that $\sim$10\% of stars
might host close binary companions within the period range accessible
by this survey, this gives a probability of 0.016 that a blended
binary star might be chance-aligned within two pixels of any given
target star.  Noting that the average number of planets per star with
periods less than 30 days is about 0.25 \citep{Fressin:2013}, we can
roughly estimate that we expect $<$10\% of our candidates to be caused
by nearby contaminating EBs.  This estimate suggests that such
astrophsycial false positives should be rare in our sample, consistent
with our detection of 2/36 candidates with clear centroid offsets.

@@

This research made use of the NASA \project{Astrophysics Data System} and the
NASA Exoplanet Archive.
The Archive is operated by the California Institute of Technology, under
contract with NASA under the Exoplanet Exploration Program.
This \paper\ includes data collected by the \kepler\ mission. Funding for the
\kepler\ mission is provided by the NASA Science Mission directorate.
These data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.

{\it Facilities:} \facility{Kepler}

>>>>

A quick \emph{a priori} estimate of the background blended eclipsing
binary rate serves as a good sanity check.  A query to the TRILEGAL
(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
line-of-sight simulation software reveals that the typical density of
field stars along the line of sight to the C1 field is about
$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
0.16 that a background star might be blended within a 8\,arcsec radius
(two pixels) from a target star.  Allowing that $\sim$10\% of stars
might host close binary companions within the period range accessible
by this survey, this gives a probability of 0.016 that a blended
binary star might be chance-aligned within two pixels of any given
target star.  Noting that the average number of planets per star with
periods less than 30 days is about 0.25 \citep{Fressin:2013}, we can
roughly estimate that we expect $<$10\% of our candidates to be caused
by nearby contaminating EBs.  This estimate suggests that such
astrophysical false positives should be rare in our sample, consistent
with our detection of 2/36 candidates with clear centroid offsets.

@@

This research made use of the NASA \project{Astrophysics Data System} and the
NASA Exoplanet Archive.
The Archive is operated by the California Institute of Technology, under
contract with NASA under the Exoplanet Exploration Program.
This \paper\ includes data collected by the \kepler\ mission. Funding for the
\kepler\ mission is provided by the NASA Science Mission directorate.
We are grateful to the entire \kepler\ team, past and present.
Their tireless efforts were all essential to the tremendous success of the mission
and the successes of \KT, present and future.
These data were obtained from the Mikulski Archive for Space Telescopes
(MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST is provided by the NASA Office of Space Science via grant
NNX13AC07G and by other grants and contracts.

{\it Facilities:} \facility{Kepler}, \facility{K2}
